maps

### 2022-11-23 code/maps.qmd
Add inset map to map of study area

```{r}
library(sf)
library(tmap)
library(stars)
library(tidyverse)
library(RPostgreSQL)
```

@@

nps_boundaries <- st_read(here::here(
  "data", "maps", "nps-boundaries", "yose_kica_sequ_boundaries.shp"))
st_crs(nps_boundaries) #determine coordinate reference system (CRS)

# California Color Hillshade (90m) from koordinates.com
hillshade <- read_stars(here::here(
  "data", "maps", "hillshade-90m", "california-color-hillshade-90m.tif"))
st_crs(hillshade)
```

@@

### Transform CRS of nps_boundary

```{r}
nps_boundaries <- st_transform(nps_boundaries, 26911)
```

@@

```{r}
bbox <- st_bbox(c(xmin = 238000, ymax = 4235000, xmax = 403000, ymin = 4011000), crs = st_crs(nps_boundaries))
hillshade_crop <- st_crop(hillshade, bbox)
hillshade_crop <- st_transform(hillshade_crop, 26911)
```

### Create map

@@

@@

```{r}
tmap_save(exome_points_map, here::here("out", "map_exome_points.png"))
```

>>>>

```{r}
library(sf)
library(tmap)
library(stars)
library(grid)
library(tidyverse)
library(RPostgreSQL)
```

@@

nps_boundaries <- st_read(here::here(
  "data", "maps", "nps-boundaries", "yose_kica_sequ_boundaries.shp"))
st_crs(nps_boundaries) # determine coordinate reference system (CRS)
nps_boundaries <- st_transform(nps_boundaries, 26911) # transform to NAD83 UTM11

# California Color Hillshade (90m) from koordinates.com
hillshade_90m <- read_stars(here::here(
  "data", "maps", "hillshade-90m", "california-color-hillshade-90m.tif"))
st_crs(hillshade_90m)

hillshade_300m <- read_stars(here::here(
  "data", "maps", "hillshade-300m", "california-color-hillshade-300m.tif"))
```

@@

@@

```{r}
bbox <- st_bbox(c(xmin = 238000, ymax = 4235000, xmax = 403000, ymin = 4011000), 
                crs = st_crs(nps_boundaries)) %>%  
  st_as_sfc()
hillshade_crop <- st_crop(hillshade_90m, bbox)
hillshade_crop <- st_transform(hillshade_crop, 26911)
```

### Create study area map

@@

### Create inset map of California

```{r}
inset_map <- tm_shape(hillshade_300m) +
  tm_rgb(r = 1, g = 2, b = 3) +
  tm_shape(bbox) + 
  tm_borders(col = "black")

inset_map
```

### Study area map with inset map

```{r}
exome_points_map
print(inset_map, vp = viewport(0.35, 0.37, width = 0.2, height = 0.2))
```

@@

```{r}
tmap_save(exome_points_map, 
          here::here("out", "map_exome_points.png"),
          insets_tm = inset_map,
          insets_vp = viewport(0.14, 0.24, width = 0.2, height = 0.2))
```

#### To Do

-   Exported CA tif has no whitespace around state, has black border. How to remove border and add whitespace?
